Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
twang

# Additional packages
library(emmeans)
library(margins)
library(survey)
library(ggplot2)
library(gridExtra)
library(knitr)
library(mitools)  # For proper MI pooling with survey weights
library(mice)     # For pooling utilities

@@

# Reshape for presentation
prob_table <- prob_summary |>
  select(ever_lapse_binary, dr_severity, any_treatment, prob, asymp.LCL, asymp.UCL) |>
  mutate(
    Probability = paste0(round(prob, 3), " (", 
                        round(asymp.LCL, 3), ", ", 
                        round(asymp.UCL, 3), ")")
  ) |>
  select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
  pivot_wider(names_from = ever_lapse_binary, values_from = Probability)

>>>>

# Additional packages
library(emmeans)
library(margins)
library(survey)
library(ggplot2)
library(gridExtra)
library(knitr)
library(tidyr)    # For pivot_wider
library(dplyr)    # For data manipulation
library(mitools)  # For proper MI pooling with survey weights
library(mice)     # For pooling utilities

@@

# Reshape for presentation
prob_table <- prob_summary |>
  select(ever_lapse_binary, dr_severity, any_treatment, prob, CI_Lower, CI_Upper) |>
  mutate(
    Probability = paste0(round(prob, 3), " (", 
                        round(CI_Lower, 3), ", ", 
                        round(CI_Upper, 3), ")")
  ) |>
  select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
  pivot_wider(names_from = ever_lapse_binary, values_from = Probability)
